On the adhesivity of EGGs

### 2025-03-03 calco/main.tex
Update main.tex

\begin{restatable}{corollary}{mn}\label{cor:mono2}
	If $(h_E, h_V, h_Q): \mathcal{G\to H}$ is a regular mono in $\EqHyp$, then $h_E, h_V$ and $h_C$ are all monos.
\end{restatable}

>>>>

\begin{restatable}{corollary}{mn}\label{cor:mono2}
	An arrow $(h_E, h_V, h_Q): \mathcal{G\to H}$ in $\EqHyp$ is a regular mono if and only if $h_E, h_V$ and $h_C$ are all monos.
\end{restatable}
